---
title: "Task4"
author: "Darya Nemirich"
date: '13 апреля 2019 г '
output: pdf_document
---
Upload the dataframe.
```{r}
weather <- readRDS("D:/Bioinformatics and System Biology/2nd term/R/R_classwork/Task4/weather.rds")
```
Let's look on the table and on the information about its variables.
```{r}
head(weather)
str(weather)
complete.cases(weather)
```
There are several NAs in the table. There is an additional column named X, which is, as I suppose, represents a day of the measurement. 
Variables are rows, not columns. Numeric observations are not numeric.

Let's get rid of X varible.
```{r}
weather$X <- NULL
```
Uploading necessary libraries
```{r}

library(tidyr)
library(dplyr)

```
Transform the data from wide to long and then vice versa. 
```{r}
weather_tidy <- gather(weather, day, value, X1:X31)
weather_tidy <- spread(weather_tidy, measure, value)
head(weather_tidy, 15)

```
Now our variables on the right places. Replace T letters in precipitation column with NA's. 
Get rid of the x letter in day number.
```{r}
weather_tidy$PrecipitationIn <- gsub('T', NA, weather_tidy$PrecipitationIn, ignore.case = TRUE)
weather_tidy <- mutate(weather_tidy, day=extract_numeric(day))
head(weather_tidy)

```
Now I will make our columns with numeric data real numeric.
```{r}

weather_tidy[,c(1,2,4,6:25)] <- lapply(weather_tidy[,c(1,2,4,6:25)], as.numeric)
str(weather_tidy)


```
Let's plot our numeric values. As we can see, there is the outlier in Max. 
Humidity column. There is an additional zero in 138 observation. Let's get rid of it.
```{r}
boxplot(weather_tidy[,c(1,2,4,6:25)])
weather_tidy$Max.Humidity
weather_tidy[138, 8] <- 100
summary(weather_tidy$Max.Humidity)
```